---
title: "Small plasmid analysis"
date: "2020-11-24"
author: "Ryan Wick"
output:
  html_document:
    pandoc_args: ["+RTS", "-K64m", "-RTS", "--self-contained",]
    df_print: paged
    keep_md: false
    toc: true
    toc_float: true
---

This document contains the R code used to generate data and plots for my paper comparing rapid and ligation kits in the context of genomes with small plasmids.

It takes as input:

* `Table_S1.xlsx` - assumed to be in the same directory as this file.
* Four TSV files of read-level information, assumed to be in a `../data` directory:
  * `tech_rep_1_ligation_reads.tsv.gz`
  * `tech_rep_1_rapid_reads.tsv.gz`
  * `tech_rep_2_ligation_reads.tsv.gz`
  * `tech_rep_2_rapid_reads.tsv.gz`
* One TSV file of sliding-window GC and depth values: `gc_and_depth.tsv.gz`

This script is licensed under a Creative Commons Attribution 4.0 International License. You should have received a copy of the license along with this work. If not, see <http://creativecommons.org/licenses/by/4.0/>.




## Setup

```{r}
library(tidyverse)
library(knitr)
library(readxl)
library(cowplot)
library(ggrastr)
```

Output settings:
```{r}
opts_chunk$set(fig.width=8, fig.height=5, dpi=300, fig.path='../plots/', echo=TRUE, dev=c('png','pdf'), warning=FALSE, message=FALSE)
pdf.options(useDingbats = FALSE)
```




## Load data

```{r}
barcode_data <- read_excel("Table_S1.xlsx", sheet = "Per-barcode", col_names = TRUE)
barcode_data$`Barcode number` <- factor(barcode_data$`Barcode number`, levels = barcode_data$`Barcode number`)

replicon_data <- read_excel("Table_S1.xlsx", sheet = "Per-replicon", col_names = TRUE)
replicon_data$size_category <- ifelse(replicon_data$Size >=20000, "big (≥20 kbp)", "small (<20 kbp)")
replicon_data$rapid_to_illumina <- replicon_data$`ONT rapid read depth (normalised to chromosome)` / replicon_data$`Illumina read depth (normalised to chromosome)`
replicon_data$ligation_to_illumina <- replicon_data$`ONT ligation read depth (normalised to chromosome)` / replicon_data$`Illumina read depth (normalised to chromosome)`

run_data <- read_excel("Table_S1.xlsx", sheet = "Per-run", col_names = TRUE)

load_read_data <- function(filename) {
  reads <- read_delim(filename, "\t", escape_double = FALSE, trim_ws = TRUE)
  reads$mean_identity <- as.numeric(sub("%", "", reads$mean_identity)) / 100.0
  reads$read_coverage <- as.numeric(sub("%", "", reads$read_coverage)) / 100.0
  reads$translocation_speed <- reads$read_length / reads$template_duration
  reads$start_time_hours <- reads$start_time / 3600
  return(reads)
}

tech_rep_1_ligation_reads <- load_read_data("../data/tech_rep_1_ligation_reads.tsv.gz")
tech_rep_1_rapid_reads <- load_read_data("../data/tech_rep_1_rapid_reads.tsv.gz")
tech_rep_2_ligation_reads <- load_read_data("../data/tech_rep_2_ligation_reads.tsv.gz")
tech_rep_2_rapid_reads <- load_read_data("../data/tech_rep_2_rapid_reads.tsv.gz")

gc_depth <- read_delim("../data/gc_and_depth.tsv.gz", "\t", escape_double = FALSE, trim_ws = TRUE)
```




## Yield

Here are the full yields:
```{r}
sum(tech_rep_1_ligation_reads$read_length, na.rm = TRUE)
sum(tech_rep_2_ligation_reads$read_length, na.rm = TRUE)
sum(tech_rep_1_rapid_reads$read_length, na.rm = TRUE)
sum(tech_rep_2_rapid_reads$read_length, na.rm = TRUE)
```



```{r}
max(tech_rep_1_ligation_reads$start_time_hours)
max(tech_rep_2_ligation_reads$start_time_hours)
max(tech_rep_1_rapid_reads$start_time_hours)
max(tech_rep_2_rapid_reads$start_time_hours)
```



Since not all runs went for the same amount of time, and some were refueled, which makes it harder to compare yields. So here are yields up to the 12-hour point (before any refueling took place):
```{r}
yield_before_hour <- function(read_table, hour_cutoff) {
  read_table %>% filter(start_time_hours < hour_cutoff) -> read_table
  return(sum(read_table$read_length))
}
```

```{r}
yield_before_hour(tech_rep_1_ligation_reads, 12)
yield_before_hour(tech_rep_2_ligation_reads, 12)
yield_before_hour(tech_rep_1_rapid_reads, 12)
yield_before_hour(tech_rep_2_rapid_reads, 12)
```





## Demultiplexing

```{r}
incorrect_demux_percent <- function(read_table) {
  
  # Filter out reads where the reference is the plasmid found in two genomes, as these are unreliable for demultiplexing.
  read_table = filter(read_table, reference_names != "Haemophilus_unknown_M1C132_1__plasmid_3")
  read_table = filter(read_table, reference_names != "Klebsiella_oxytoca_MSB1_2C__plasmid_3")

  correct <- sum(read_table$demultiplex_status == 'correct', na.rm = TRUE)
  incorrect <- sum(read_table$demultiplex_status == 'incorrect', na.rm = TRUE)
  
  incorrect_unused <- sum(read_table$demultiplex_status == 'incorrect' &
                          (read_table$barcode_arrangement == 'barcode06' |
                           read_table$barcode_arrangement == 'barcode09' |
                           read_table$barcode_arrangement == 'barcode10' |
                           read_table$barcode_arrangement == 'barcode11' |
                           read_table$barcode_arrangement == 'barcode12'), na.rm = TRUE)
  
  incorrect_used <- sum(read_table$demultiplex_status == 'incorrect' &
                        (read_table$barcode_arrangement == 'barcode01' |
                         read_table$barcode_arrangement == 'barcode02' |
                         read_table$barcode_arrangement == 'barcode03' |
                         read_table$barcode_arrangement == 'barcode04' |
                         read_table$barcode_arrangement == 'barcode05' |
                         read_table$barcode_arrangement == 'barcode07' |
                         read_table$barcode_arrangement == 'barcode08'), na.rm = TRUE)
  
  total <- correct + incorrect
  return(c(100.0 * incorrect_unused / total,
           100.0 * incorrect_used / total,
           100.0 * incorrect / total))
}
```

```{r}
incorrect_demux_percent(tech_rep_1_ligation_reads)
incorrect_demux_percent(tech_rep_2_ligation_reads)
incorrect_demux_percent(tech_rep_1_rapid_reads)
incorrect_demux_percent(tech_rep_2_rapid_reads)
```

I was curious is selecting for high quality reads fixed bad demuxing, so I tried creating high quality subsets based on `barcode_score`, `mean_qscore_template` and `mean_identity`. However, none of these reliably resulted in a significant improvement.





## Chimeras

```{r}
chimera_percent <- function(read_table) {
  total <- dim(read_table)[1]
  
  all_chimeras <- sum(read_table$chimera == 'yes', na.rm = TRUE)
  all_chimeras_percent <- 100.0 * all_chimeras / total
  
  within_bin_chimeras <- sum(read_table$within_bin_chimera == 'yes', na.rm = TRUE)
  within_bin_chimeras_percent <- 100.0 * within_bin_chimeras / total
  
  cross_bin_chimeras <- sum(read_table$cross_bin_chimera == 'yes', na.rm = TRUE)
  cross_bin_chimeras_percent <- 100.0 * cross_bin_chimeras / total
  
  return(c(within_bin_chimeras_percent,
           cross_bin_chimeras_percent,
           all_chimeras_percent))
}
```

```{r}
chimera_percent(tech_rep_1_ligation_reads)
chimera_percent(tech_rep_2_ligation_reads)
chimera_percent(tech_rep_1_rapid_reads)
chimera_percent(tech_rep_2_rapid_reads)
```




## ONT vs Illumina read depth

This compares the normalised Illumina and ONT read depths for plasmids, which are classified as either 'big' or 'small'.

A regression line and r-squared value are included. The regression line for the ligation kit is well below the y=x diagonal and have a weaker r-squared. The line for the rapid kit is close to the y=x diagonal and has a stronger r-squared.

```{r ont_vs_illumina_depth, fig.width = 8, fig.height = 3.75, useDingbats = FALSE}
# https://stackoverflow.com/a/13451587/2438989
r_squared_text = function(m) {
  l <- list(r2 = format(summary(m)$r.squared, digits = 3));
  eq <- substitute(italic(r)^2~"="~r2, l)
  as.character(as.expression(eq));                 
}

ont_vs_illumina_depth <- function(replicon_data, column_name, plot_title, y_title, point_colour, line_colour, line_fill_colour, regression) {
  column_name <- sym(column_name)

  p <- ggplot(replicon_data, aes(x=`Illumina read depth (normalised to chromosome)`, y=!!column_name)) +
    geom_abline(linetype = "dashed", colour = "#CCCCCC") +
    geom_smooth(method='lm', colour=line_colour, fill=line_fill_colour, size=0.5, se = FALSE) +
    geom_point(colour = point_colour, aes(shape=size_category)) +
    annotate("text", x = 3.2, y = 320, label = r_squared_text(regression), parse = TRUE, colour=line_colour) +
    theme_bw() + theme(plot.background = element_blank(), legend.position = "none") +
    scale_x_log10(breaks = c(0.1, 1, 10, 100, 1000), labels = c("0.1", "1", "10", "100", "1000"), minor_breaks = NULL, expand = c(0, 0)) +
    scale_y_log10(breaks = c(0.1, 1, 10, 100, 1000), labels = c("0.1", "1", "10", "100", "1000"), minor_breaks = NULL, expand = c(0, 0)) +
    coord_fixed(xlim = c(0.1, 1000), ylim = c(0.1, 1000)) +
    labs(x = "Illumina read depth", y = y_title, title = plot_title)
}

replicon_data_no_chromosome <- filter(replicon_data, Replicon != "chromosome")
replicon_data_no_chromosome$ligation_log_depth <- log10(replicon_data_no_chromosome$`ONT ligation read depth (normalised to chromosome)`)
replicon_data_no_chromosome$rapid_log_depth <- log10(replicon_data_no_chromosome$`ONT rapid read depth (normalised to chromosome)`)
replicon_data_no_chromosome$illumina_log_depth <- log10(replicon_data_no_chromosome$`Illumina read depth (normalised to chromosome)`)

# Log-based regressions
ligation_to_illumina <- lm(ligation_log_depth ~ illumina_log_depth * Size, data=replicon_data_no_chromosome)
rapid_to_illumina <- lm(rapid_log_depth ~ illumina_log_depth, data=replicon_data_no_chromosome)
rapid_to_ligation <- lm(rapid_log_depth ~ ligation_log_depth, data=replicon_data_no_chromosome)

summary(ligation_to_illumina)
summary(rapid_to_illumina)

p1 <- ont_vs_illumina_depth(replicon_data_no_chromosome, "ONT ligation read depth (normalised to chromosome)",
                            "Oxford Nanopore vs Illumina sequencing read depths for plasmids\n",
                            "ONT ligation read depth", "#CB4D42", "#760000", "#FFD7D5", ligation_to_illumina)
p2 <- ont_vs_illumina_depth(replicon_data_no_chromosome, "ONT rapid read depth (normalised to chromosome)",
                            "", "ONT rapid read depth", "#00989D", "#00555A", "#B3EDEF", rapid_to_illumina)

plot_grid(p1, p2, ncol = 2, align="hv")
```

I did experiment with using GC-corrected Illumina depths, i.e. adjusting the Illumina depths to compensate for the GC bias of that platform. But it only made a tiny insignificant difference (and complicated the method) so I opted against it.


This plot shows the same data, but instead using the normalised depths directly, it uses the ONT/Illumina depth ratio.

```{r depth_vs_plasmid_size_grouped, fig.width = 6.5, fig.height = 4, useDingbats = FALSE}
depth_ratios <- data.frame(replicon_data$Replicon)
depth_ratios$rapid_to_illumina <- replicon_data$rapid_to_illumina
depth_ratios$ligation_to_illumina <- replicon_data$ligation_to_illumina
depth_ratios$size_category <- replicon_data$size_category
colnames(depth_ratios) <- c("Replicon", "rapid", "ligation", "size")
depth_ratios %>% filter(Replicon != "chromosome") %>% drop_na() %>% select(-Replicon) -> depth_ratios
depth_ratios %>% gather(prep, ratio, -size) -> depth_ratios
depth_ratios$size <- factor(depth_ratios$size, levels = c("small (<20 kbp)", "big (≥20 kbp)"))
depth_ratios %>% filter(prep == "rapid") -> rapid_depth_ratios
depth_ratios %>% filter(prep == "ligation") -> ligation_depth_ratios

small_big_depth_ratios <- function(depth_ratios, plot_title, y_title, point_colour) {
  p <- ggplot(depth_ratios, aes(x = size, y = ratio)) +
    geom_hline(yintercept=1, linetype="dashed", colour = "#888888") +
    geom_dotplot(binwidth=0.1, binaxis = "y", stackdir = "center", fill=point_colour, colour=NA) +
    theme_bw() + theme(plot.background = element_blank()) +
    scale_y_log10(breaks = c(0.01, 0.1, 1, 10), labels = c("0.01", "0.1", "1", "10"), minor_breaks = NULL) +
    coord_fixed(ylim = c(0.007, 10), ratio=0.8) +
    labs(x = "Plasmid size", y = y_title, title = plot_title)
  return(p)
}
  
p1 <- small_big_depth_ratios(ligation_depth_ratios, "Oxford Nanopore vs Illumina sequencing read depths for plasmids\n",
                             "Ligation:Illumina read depth ratio", "#CB4D42")
p2 <- small_big_depth_ratios(rapid_depth_ratios, "",
                             "Rapid:Illumina read depth ratio", "#00989D")

plot_grid(p1, p2, ncol = 2, align="hv")
```


This plot once again shows the same data, but puts plasmid size as a continuous variable on the x axis (instead of categorical). I liked this one best and it is thus used in the main text.

```{r depth_vs_plasmid_size, fig.width = 8, fig.height = 3.75, useDingbats = FALSE}
depth_ratios <- data.frame(replicon_data$Replicon)
depth_ratios$Size <- replicon_data$Size
depth_ratios$size_log <- log10(depth_ratios$Size)
depth_ratios$rapid_to_illumina <- replicon_data$rapid_to_illumina
depth_ratios$rapid_to_illumina_log <- log10(depth_ratios$rapid_to_illumina)
depth_ratios$ligation_to_illumina <- replicon_data$ligation_to_illumina
depth_ratios$ligation_to_illumina_log <- log10(depth_ratios$ligation_to_illumina)
colnames(depth_ratios) <- c("replicon", "size", "size_log", "rapid", "rapid_log", "ligation", "ligation_log")
depth_ratios %>% filter(replicon != "chromosome") %>% drop_na() %>% select(-replicon) -> depth_ratios

size_depth_ratios <- function(depth_ratios, column_name, plot_title, y_title, point_colour) {
  column_name <- sym(column_name)

  p <- ggplot(depth_ratios, aes(x = size, y = !!column_name)) +
    geom_hline(yintercept=1, linetype="dashed", colour = "#888888") +
    # geom_smooth(method='lm', size=0.5, se = FALSE, colour=point_colour) +
    geom_point(colour = point_colour) +
    theme_bw() + theme(plot.background = element_blank()) +
    scale_x_log10(breaks = c(1000, 3000, 10000, 30000, 100000, 300000), labels = c("1", "3", "10", "30", "100", "300"), minor_breaks = NULL, expand=c(0, 0)) +
    scale_y_log10(breaks = c(0.01, 0.1, 1, 10), labels = c("0.01", "0.1", "1", "10"), minor_breaks = NULL) +
    coord_fixed(xlim = c(1000, 300000), ylim = c(0.007, 10), ratio=0.7) +
    labs(x = "Plasmid size (kbp)", y = y_title, title = plot_title)
    
  return(p)
}
  
p1 <- size_depth_ratios(depth_ratios, "ligation",
                        "Oxford Nanopore vs Illumina sequencing read depths for plasmids\n",
                        "Ligation:Illumina read depth ratio", "#CB4D42")
p2 <- size_depth_ratios(depth_ratios, "rapid", "",
                        "Rapid:Illumina read depth ratio", "#00989D")

plot_grid(p1, p2, ncol = 2, align="hv")
```

I wanted p-values for whether or not there is a relationship between plasmid size and the ONT/Illumina depth ratio. I.e. the null hypothesis is that the slope = 0.

```{r}
ligation_to_size <- lm(ligation_log ~ size_log, data=depth_ratios)
rapid_to_size <- lm(rapid_log ~ size_log, data=depth_ratios)

summary(ligation_to_size)
summary(rapid_to_size)
```

The results are pretty clear! For ligation (p = 1.87e-12), there is a strong relationship. For rapid (p = 0.417), there isn't.


Calculating the mean/min underrepresentation of <10 kbp plasmids in ligation reads (I report this value in the text):
```{r}
small_plasmid_depth_ratios <- filter(depth_ratios, size < 20000)
mean(small_plasmid_depth_ratios$ligation)
min(small_plasmid_depth_ratios$ligation)

small_plasmid_depth_ratios <- filter(depth_ratios, size < 3000)
mean(small_plasmid_depth_ratios$ligation)
min(small_plasmid_depth_ratios$ligation)
```


## Barcode distributions

```{r barcode_yields, fig.width = 8, fig.height = 8, useDingbats = FALSE}
barcode_distribution <- function(barcode_data, column_name, plot_title, fill_colour, max_y) {
  column_name <- sym(column_name)
  wrong_colour = "#999999"
  unclassified_colour = "#666666"
  
  p <- ggplot(barcode_data) +
    geom_bar(aes(x=`Barcode number`, y=!!column_name, fill=`Barcode number`), stat = "identity") +
    theme_bw() + theme(plot.background = element_blank()) +
    scale_fill_manual(values = c("1" = fill_colour, "2" = fill_colour, "3" = fill_colour,
                                 "4" = fill_colour, "5" = fill_colour, "6" = wrong_colour,
                                 "7" = fill_colour, "8" = fill_colour, "9" = wrong_colour,
                                 "10" = wrong_colour, "11" = wrong_colour, "12" = wrong_colour,
                                 "unclassified" = unclassified_colour)) +
    guides(fill = FALSE) +
    scale_y_log10(breaks = c(1, 10, 100, 1000, 10000, 100000, 1000000, 10000000),
                  labels = c(bquote(10^0), bquote(10^1), bquote(10^2), bquote(10^3), bquote(10^4), bquote(10^5), bquote(10^6), bquote(10^7)),
                  minor_breaks = NULL,
                  expand = c(0, 0)) +
    coord_cartesian(ylim = c(1, max_y)) +
    labs(x = "Barcode", y = "Read count", title = plot_title)
}


p1 <- barcode_distribution(barcode_data, "Ligation (run 1) read count", "Ligation (run 1)", "#CB4D42", 10000000)
p2 <- barcode_distribution(barcode_data, "Ligation (run 2) read count", "Ligation (run 2)", "#CB4D42", 10000000)
p3 <- barcode_distribution(barcode_data, "Rapid (run 1) read count", "Rapid (run 1)", "#00989D", 10000000)
p4 <- barcode_distribution(barcode_data, "Rapid (run 2) read count", "Rapid (run 2)", "#00989D", 10000000)

plot_grid(p1, p2, p3, p4, ncol = 1, align="hv")
```





## Barcode N50s

```{r barcode_n50s, fig.width = 8, fig.height = 5, useDingbats = FALSE}
barcode_n50s <- function(barcode_data, column_name, plot_title, fill_colour, max_y) {
  barcode_data_real_barcodes <- filter(barcode_data, `Barcode number` != "6" & `Barcode number` != "9" &
                                                     `Barcode number` != "10" & `Barcode number` != "11" &
                                                     `Barcode number` != "12" & `Barcode number` != "unclassified")

  column_name <- sym(column_name)
  wrong_colour = "#999999"
  unclassified_colour = "#666666"
  
  p <- ggplot(barcode_data_real_barcodes) +
    geom_bar(aes(x=`Barcode number`, y=!!column_name, fill=`Barcode number`), stat = "identity") +
    theme_bw() + theme(plot.background = element_blank()) +
    scale_fill_manual(values = c("1" = fill_colour, "2" = fill_colour, "3" = fill_colour,
                                 "4" = fill_colour, "5" = fill_colour, "6" = wrong_colour,
                                 "7" = fill_colour, "8" = fill_colour, "9" = wrong_colour,
                                 "10" = wrong_colour, "11" = wrong_colour, "12" = wrong_colour,
                                 "unclassified" = unclassified_colour)) +
    guides(fill = FALSE) +
    scale_y_continuous(expand = c(0, 0), breaks = c(0, 10000, 20000, 30000), labels = c("0", "10k", "20k", "30k")) + 
    coord_cartesian(ylim = c(0, max_y)) +
    labs(x = "Barcode", y = "Read N50", title = plot_title)
}


p1 <- barcode_n50s(barcode_data, "Ligation (run 1) read N50", "Ligation (run 1)", "#CB4D42", 30000)
p2 <- barcode_n50s(barcode_data, "Ligation (run 2) read N50", "Ligation (run 2)", "#CB4D42", 30000)
p3 <- barcode_n50s(barcode_data, "Rapid (run 1) read N50", "Rapid (run 1)", "#00989D", 30000)
p4 <- barcode_n50s(barcode_data, "Rapid (run 2) read N50", "Rapid (run 2)", "#00989D", 30000)

plot_grid(p1, p2, p3, p4, ncol = 2, align="hv")
```

This has the same data as the previous plot, but in a grouped bar format:
```{r barcode_n50s_grouped, fig.width = 8, fig.height = 4, useDingbats = FALSE}
barcode_data_real_barcodes <- filter(barcode_data, `Barcode number` != "6" & `Barcode number` != "9" &
                                                   `Barcode number` != "10" & `Barcode number` != "11" &
                                                   `Barcode number` != "12" & `Barcode number` != "unclassified")
barcode_data_real_barcodes = subset(barcode_data_real_barcodes, select = c(`Barcode number`,
                                                                           `Ligation (run 1) read N50`, `Rapid (run 1) read N50`,
                                                                           `Ligation (run 2) read N50`, `Rapid (run 2) read N50`))
colnames(barcode_data_real_barcodes) <- c("Num", "Ligation 1", "Rapid 1", "Ligation 2", "Rapid 2")
barcode_data_real_barcodes <- barcode_data_real_barcodes %>% pivot_longer(-Num, names_to = "Sequencing run", values_to = "N50")
barcode_data_real_barcodes$`Sequencing run` <- factor(barcode_data_real_barcodes$`Sequencing run`, levels = c("Ligation 1", "Rapid 1", "Ligation 2", "Rapid 2"))

ggplot(barcode_data_real_barcodes) +
    geom_bar(aes(x=Num, y=N50, fill=`Sequencing run`), stat = "identity", position = "dodge") +
    theme_bw() + theme(plot.background = element_blank()) +
    scale_fill_manual(values = c("Ligation 1" = "#CB4D42", "Rapid 1" = "#00989D",
                                 "Ligation 2" = "#E58E8C", "Rapid 2" = "#52CCCC")) +
    scale_y_continuous(expand = c(0, 0), breaks = c(0, 10000, 20000, 30000), labels = c("0", "10k", "20k", "30k")) +
    coord_cartesian(ylim = c(0, 30000)) +
    labs(x = "Barcode number", y = "Read N50", title = "Per-barcode read N50 lengths")
```




## Read identity distributions

```{r identity_distributions, fig.width = 8, fig.height = 8, useDingbats = FALSE}
identity_distribution <- function(read_table, plot_title, fill_colour, line_colour) {
  read_table %>% filter(mean_identity > 0.5) -> read_table
  read_table %>% filter(read_length > 10000) -> read_table
  read_table %>% filter(read_coverage > 0.9) -> read_table
  
  # Optionally, filter for reads with a good translocation speed.
  # read_table %>% filter(translocation_speed > 380) -> read_table
  # read_table %>% filter(translocation_speed < 400) -> read_table
  
  median_identity <- median(read_table$mean_identity)
  
  p <- ggplot(read_table) +
    geom_density(aes(x = mean_identity, y = ..scaled..), bw = 0.0025, fill = fill_colour, colour = NA) +
    geom_vline(aes(xintercept = median_identity), alpha = 0.75, linetype = "dashed", colour = line_colour) + 
    theme_bw() +  theme(plot.background = element_blank()) +
    coord_cartesian(xlim = c(0.85, 1.0), ylim = c(0, 1.1)) +
    scale_x_continuous(breaks = seq(0.85, 1, 0.01),
                       labels = paste(seq(85, 100, 1), "%", sep = ""),
                       expand = c(0.002, 0.002)) +
    scale_y_continuous(breaks = NULL, expand = c(0, 0)) +
    labs(title = plot_title, x = "read identity", y = NULL)
  
  return(p)
}

p1 <- identity_distribution(tech_rep_1_ligation_reads, "Ligation (run 1)", "#F8766D", "#760000")
p2 <- identity_distribution(tech_rep_2_ligation_reads, "Ligation (run 2)", "#F8766D", "#760000")
p3 <- identity_distribution(tech_rep_1_rapid_reads, "Rapid (run 1)", "#00BFC4", "#00555A")
p4 <- identity_distribution(tech_rep_2_rapid_reads, "Rapid (run 2)", "#00BFC4", "#00555A")

plot_grid(p1, p2, p3, p4, ncol = 1, align="hv")
```




## Translocation speed distributions

```{r translocation_speed_distributions, fig.width = 8, fig.height = 8, useDingbats = FALSE}
translocation_speed_distribution <- function(read_table, plot_title, fill_colour) {
  read_table %>% filter(mean_identity > 0.5) -> read_table
  read_table %>% filter(read_length > 10000) -> read_table
  
  p <- ggplot(read_table, aes(translocation_speed)) +
    geom_density(fill = fill_colour, colour = NA) +
    theme_bw() + theme(plot.background = element_blank()) +
    coord_cartesian(xlim = c(0, 600)) +
    scale_x_continuous(breaks = seq(0, 600, 100),
                       expand = c(0.02, 0.02)) +
    scale_y_continuous(breaks = NULL) +
    labs(title = plot_title, x = NULL, y = NULL)
  
  return(p)
}

p1 <- translocation_speed_distribution(tech_rep_1_ligation_reads, "Ligation 1 translocation speed", "#F8766D")
p2 <- translocation_speed_distribution(tech_rep_2_ligation_reads, "Ligation 2 translocation speed", "#F8766D")
p3 <- translocation_speed_distribution(tech_rep_1_rapid_reads, "Rapid 3 translocation speed", "#00BFC4")
p4 <- translocation_speed_distribution(tech_rep_2_rapid_reads, "Rapid 4 translocation speed", "#00BFC4")

plot_grid(p1, p2, p3, p4, ncol = 1, align="hv")
```




## Identity vs translocation speed

```{r identity_vs_translocation_speed_plots, fig.width = 8, fig.height = 8, useDingbats = FALSE}
identity_vs_translocation_speed <- function(read_table, plot_title, point_colour) {
  read_table %>% filter(mean_identity > 0.5) -> read_table
  read_table %>% filter(read_length > 10000) -> read_table
  
  read_table <- read_table[0:50000,]  # so we don't have too many points

  p <- ggplot(read_table) +
    rasterise(geom_point(aes(x=translocation_speed, y=mean_identity), colour=point_colour, alpha=0.15, shape=16, size=0.5), dpi=600) +
    theme_bw() + theme(plot.background = element_blank()) +
    scale_y_continuous(breaks = seq(0.9, 1, 0.02),
                       labels = paste(seq(90, 100, 2), "%", sep = "")) +
    scale_x_continuous(breaks = seq(0, 600, 100)) +
    coord_cartesian(xlim = c(0, 600), ylim = c(0.9, 1)) +
    labs(title = plot_title, x = "translocation speed (bp/sec)", y = "identity")
  
  return(p)
}

p1 <- identity_vs_translocation_speed(tech_rep_1_ligation_reads, "Ligation (run 1)", "#CB4D42")
p2 <- identity_vs_translocation_speed(tech_rep_2_ligation_reads, "Ligation (run 2)", "#CB4D42")
p3 <- identity_vs_translocation_speed(tech_rep_1_rapid_reads, "Rapid (run 1)", "#00989D")
p4 <- identity_vs_translocation_speed(tech_rep_2_rapid_reads, "Rapid (run 2)", "#00989D")

plot_grid(p1, p2, p3, p4, ncol = 2, align="hv")
```




## Identity vs read time

```{r identity_vs_read_time_plots, fig.width = 8, fig.height = 8, useDingbats = FALSE}
max_time <- 24

identity_vs_start_time <- function(read_table, plot_title, point_colour) {
  read_table %>% filter(start_time_hours < max_time) -> read_table
  read_table %>% filter(mean_identity > 0.5) -> read_table
  read_table %>% filter(read_length > 10000) -> read_table
  
  read_table <- read_table[0:100000,]  # so we don't have too many points

  p <- ggplot(read_table) +
    rasterise(geom_point(aes(x=start_time_hours, y=mean_identity), colour=point_colour, alpha=0.05, shape=16, size=0.5), dpi=600) +
    theme_bw() + theme(plot.background = element_blank()) +
    scale_y_continuous(breaks = seq(0.9, 1, 0.02),
                       labels = paste(seq(90, 100, 2), "%", sep = "")) +
    scale_x_continuous(breaks = seq(0, max_time, 6),
                       expand = c(0, 0)) +
    coord_cartesian(xlim = c(0, max_time), ylim = c(0.92, 1)) +
    labs(title = plot_title, x = "read time (hours)", y = "identity")
  
  return(p)
}

p1 <- identity_vs_start_time(tech_rep_1_ligation_reads, "Ligation (run 1)", "#CB4D42")
p2 <- identity_vs_start_time(tech_rep_2_ligation_reads, "Ligation (run 2)", "#CB4D42")
p3 <- identity_vs_start_time(tech_rep_1_rapid_reads, "Rapid (run 1)", "#00989D")
p4 <- identity_vs_start_time(tech_rep_2_rapid_reads, "Rapid (run 2)", "#00989D")

plot_grid(p1, p2, p3, p4, ncol = 2, align="hv")
```




## Translocation speed vs read time

Trying the same idea as the previous one, but now with the read's start time.

```{r translocation_speed_vs_read_time_plots, fig.width = 8, fig.height = 8, useDingbats = FALSE}
max_time <- 24

translocation_speed_vs_start_time <- function(read_table, plot_title, point_colour) {
  read_table %>% filter(start_time_hours < max_time) -> read_table
  read_table %>% filter(mean_identity > 0.5) -> read_table
  read_table %>% filter(read_length > 10000) -> read_table
  
  read_table <- read_table[0:50000,]  # so we don't have too many points

  p <- ggplot(read_table) +
    rasterise(geom_point(aes(x=start_time_hours, y=translocation_speed), colour=point_colour, alpha=0.15, shape=16, size=0.25), dpi=600) +
    theme_bw() + theme(plot.background = element_blank()) +
    scale_y_continuous(breaks = seq(0, 600, 100)) +
    scale_x_continuous(breaks = seq(0, max_time, 6),
                       expand = c(0, 0)) +
    coord_cartesian(xlim = c(0, max_time), ylim = c(0, 600)) +
    labs(title = plot_title, x = "read time (hours)", y = "translocation speed (bp/sec)")
  
  return(p)
}

p1 <- translocation_speed_vs_start_time(tech_rep_1_ligation_reads, "Ligation (run 1)", "#CB4D42")
p2 <- translocation_speed_vs_start_time(tech_rep_2_ligation_reads, "Ligation (run 2)", "#CB4D42")
p3 <- translocation_speed_vs_start_time(tech_rep_1_rapid_reads, "Rapid (run 1)", "#00989D")
p4 <- translocation_speed_vs_start_time(tech_rep_2_rapid_reads, "Rapid (run 2)", "#00989D")

plot_grid(p1, p2, p3, p4, ncol = 2, align="hv")
```




## Illumina GC bias

```{r illumina_gc_plot, fig.width = 7, fig.height = 5, useDingbats = FALSE}
replicon_data %>% filter(Replicon != "chromosome") -> plasmid_data
plasmid_gc_values <- data.frame(sort(unique(plasmid_data$GC)) * 100)
colnames(plasmid_gc_values) <- c("GC")

p1 <- ggplot(plasmid_gc_values, aes(x = GC)) +
  geom_dotplot(binwidth = 0.5, fill = "#00B0F6", colour = "#0054AA") +
  theme_bw() +
  theme(plot.background = element_blank(),
        axis.text.x=element_blank(), axis.ticks.x=element_blank(), panel.border = element_blank(),
        axis.title.y = element_text(colour = "#0054AA"),
        plot.margin = margin(0, 0, 0, 0)) +
  labs(title = "Illumina GC bias", x = NULL, y = "plasmids") +
  scale_x_continuous(breaks = NULL, expand = c(0, 0)) +
  scale_y_continuous(breaks = NULL) +
  coord_cartesian(xlim = c(28.2, 71.8))

p2 <- ggplot(gc_depth, aes(x=gc, y=depth)) +
  rasterise(geom_point(colour="#6FA100", alpha=0.2, shape=16, size=0.3), dpi=600) +
  geom_smooth(method="loess", colour="#235400", size=0.75, se = FALSE, fullrange = TRUE) +
  theme_bw() +
  theme(plot.background = element_blank(),
        plot.margin = margin(0, 0, 0, 0)) +
  scale_x_continuous(breaks = seq(0, 100, 5), expand = c(0, 0)) +
  scale_y_continuous(breaks = seq(0, 2, 0.1), expand = c(0, 0)) +
  coord_cartesian(xlim = c(28.2, 71.8), ylim = c(0.5, 1.5)) +
  labs(x = "GC content (%)", y = "Relative read depth")

plot_grid(p1, p2, ncol = 1, rel_heights = c(1, 4), align="hv")
```